\documentclass[margin,line]{res}

\usepackage{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Andrew Quitadamo \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
8700 Pinnacle Cross Dr Apt 17  \\                    
Huntersville, NC \\
aquitada@uncc.edu\\       


\section{\sc Education}
{\bf University of North Carolina at Charlotte}, Charlotte, North Carolina USA\\

\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Student, Bioinformatics and Genomics, August 2013 - present
\end{list1}


{\bf University of New Hampshire}, Durham, New Hampshire USA\\ 
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Biochemistry, Molecular and Cellular Biology,  May, 2013
\end{list1}


\section{\sc Honors and Awards} 
University Scholar 2012, 2013


\section{\sc Research Experience}
{\bf University of North Carolina at Charlotte}\\
%\vspace{-.3cm}
{\em Shi Lab} \hfill {\bf January 2014 - present}\\
Developing network models of gene interactions, and eQTL analyses in cancer.

%\vspace{-.1cm}
{\em Janies Lab} \hfill {\bf August 2013 - December 2013}\\
Created a phylogenetic tree of Phlebotominae sandflies using multiple genetic markers.    
\hspace*{.05in} 

{\bf University of New Hampshire}\\
%\vspace{-.3cm}
%\vspace{-.1cm}
{\em Thomas Lab} \hfill {\bf June 2012 - June 2013}\\
Undergraduate research assistant, studied DNA methylation in {\em C. elegans}.\\ 


\section{\sc Teaching Experience}

{\em Teaching Assistant} \hfill {\bf January 2015-May 2015}\\
BINF 6112/8112 - Bioinformatics Programming II\\
Taught lab section of Python programming

{\em Undergraduate Teaching Assistant} \hfill {\bf January 2013-May 2013}\\
Supervised BMCB 755 - Laboratory in Biochemistry and Molecular Biology

{\em PLTL Leader} \hfill {\bf September 2011 - May 2012}\\
Tutored small groups of students in introductory undergraduate physics.

\section{\sc Publications}

Quitadamo A, Desai H, and Shi X. "Network Driven Analysis of eQTLs in Lung Adenocarcinoma Subtypes". Poster, Presented at: ACMG Clinical Genetics Meeting: 2016, March 8-12; Tampa FL.

Hall B, Quitadamo A, and Shi X. "An Integrative Network Mining Approach in Colorectal Cancer". Poster, Presented at: ACMG Clinical Genetics Meeting: 2016, March 8-12; Tampa FL.

Sudmant PH, Rausch T, Gardner EJ, Handsaker RE, Abyzov A, Huddleston J, Zhang Y, Ye K, Jun G, Fritz M, Konkel MK, Malhotra A, Stütz AM, Shi X, Casale FP, Chen J, Hormozdiari F, Dayama G, Chen K, Malig M, Chaisson M, Walter K, Meiers S, Kashin S, Garrison E, Auton A, Lam H, Mu XJ, Alkan C, Antaki D, Bae T, Chines P, Chong Z, Clarke L, Dal E, Ding L, Emery S, Fan X, Gujral M, Kahveci F, Kidd JM, Kong Y, Lameijer E-W, McCarthy S, Flicek P, Gibbs RA, Marth G, Menelaou A, Muzny DM, Nelson BJ, Noor A, Parrish NF, Quitadamo A, Raeder B, Schadt E, Schlattl A, Shabalin AA, Untergasser A, Walker JA, Wang M, Yu Y, Zhang C, Zhang J, Zheng-Bradley X, Zhou W, Zichner T, Sebat J, Batzer MA, McCarroll SA, The 1000 Genomes Project Consortium, Mills RE, Gerstein MB, Bashir A, Stegle O, Devine SE, Lee C, Eichler EE, Korbel JO. “An integrated map of structural variation in 2,504 human genomes”. Nature 2015. 562: 75-81. doi:10.1038/nature15394

The 1000 Genomes Project Consortium. "A Global Reference for Human Genetic Variation". Nature 2015. 562: 68-74. doi:10.1038/nature15393

Grace-Lema DM, Yared S, Quitadamo A, Janies DA, Wheeler WC, Balkew M, Hailu A, Warburg A, Clouse RM. "A phylogeny of sand flies (Diptera: Psychodidae: Phlebotominae), using recent Ethiopian collections and a broad selection of publicly available DNA sequence data". Systematic Entomology 2015, 40(4): 733-744. doi:10.1111/syen.12135

B Hall, A Quitadamo, X Shi. "A Graph Community Approach for Constructing microRNA Networks". Big Data Computing and Communications, 283-293. doi:10.1007/978-3-319-22047-5\_23


Hall B, Quitadamo A, Shi X. "A Network Ensemble of microRNA and Gene Expression in Ovarian Cancer". Poster, Presented at: Biology of Genomes: 2015 May 5-9; Cold Spring Harbor Laboratory. 

Quitadamo A, Tian L, Hall B, Shi X. "An Integrated Network of microRNA and Gene Expression in Ovarian Cancer". BMC Bioinformatics 2015, 16(Suppl 5):S5. doi:10.1186/1471-2105-16-S5-S5

Tian L, Quitadamo A, Lin F, Shi X. "Methods for Population Based eQTL Analysis in Human Genetics". Tsinghua Science and Technology, 2014. 19(6): 624-634. doi:10.1109/TST.2014.6961031

Quitadamo A, Tian L, Shi X. "A Network Approach for Integrative Analysis of Genomic Data in Ovarian Cancer". Poster, Presented at: Intelligent Systems for Molecular Biology: 2014 July 13-15; Boston MA.

Quitadamo A, Lin F, Tian L, and Shi X. "A microRNA-Gene Network in Ovarian Cancer from Genome-Wide QTL Analysis". The 10th International Symposium on Bioinformatics Research and Applications (ISBRA2014), Zhangjiajie, China, June 28-30, 2014.

Van Note A, Quitadamo A, Piemonte A, Ramsdell J, Cocchiola A, Okamoto K, Thomas WK. “Role of DNA Methylation in Transposable Element Mobilization in {\em Caenorbabditis elegans}”. Poster, Presented at: 14th Annual Undergraduate Research Conference; 2013 Apr 12-27; Durham, NH.

\section{\sc Social Media}

Professional Blog: \href{https://andrewquitadamo.github.io/blog}{andrewquitadamo.github.io/blog}

LinkedIn: \href{http://linkedin.com/in/andrewquitadamo}{linkedin.com/in/andrewquitadamo}

Github: \href{https://github.com/andrewquitadamo}{github.com/andrewquitadamo}

Twitter: \href{https://twitter.com/andrewquitadamo}{@andrewquitadamo}

\end{resume}
\end{document}
